---
title: "Functions"
author: "Noah Siegel"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output: html_notebook
---


### Functions

The function `lag` is part of base...
```{r}
lag
find("lag")
```

However, it is also a part of the package dplyr. So when when we try to find `lag` after reading in dplyr we see the function is found in 2 different location.
```{r}
library(dplyr)
find("lag")

# Remove dplyr
detach(name = package:dplyr, unload = TRUE)
```

When we load a package in R, it gets added to the search path.
```{r}
library(dplyr)
search()
```
What if we want to use functions with similar names and that are part of different packages. Normally, we have to use `::` to specify which package to read a function form. We can also just tell R load dplyr later in the search path.
```{r}
# Remove dplyr
detach(name = package:dplyr, unload = TRUE)

library(dplyr, pos = 12)
lag
```
Now when we print the lag function, we see is it the function from `stats` namespaces.

Even for loops are functions in r. And to create a function, one needs to use the function called function.
```{r}
`for`
class(`for`)
```
```{r}
`function`
class(`function`)
```

When we create a function using the function function a call is generated.
```{r}
e = quote(function(x) x + 1)
class(e)
```
But when we evaluate the call, it is interpreted as a function.
```{r}
class(eval(e))
```
### Environemnts

Environments are a type of class in R.
```{r}
env2 = parent.env(globalenv())
class(env2)
parent.env(globalenv())
```

It is important to note that every function has an environment.
```{r}
f = function(x) x + a
environment(f)
```

```{r}
e = quote(T <- T+2)
class(e)
`<-`
```
How do we create an environment?

```{r}
env = new.env()

# Just like globalenv, env is also an environment
class(env)
# And the new environment has nothing in it..
ls(env)
```
Now that we are in the new enviroment we can add variables to it...
```{r}
env$a = list(x = 1)
env$b = 5
env$c = 10

ls(env)
```
When we change something in `a` we only see a change in the global environment.
```{r}
a = list(x = 1)
a$y = "a string"
find("a")
```
The `browser()` function opens the debugger in R.
```{r}
f = function(T) {browser() ;T = T + 2; 1 }
f(11)
```
```{r}
debug(`[`)
scatter.smooth(mtcars[, c("wt","mpt")])
```


```{r}
scatter.smooth
```

```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

