---
title: "Day 4"
author: "Noah Siegel"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output: html_notebook
---

## Evaluation
Memory issues:
Consider the following function...
Because the function calls for 1000 iterations a lot of memory is use. Typically this is not an issue however, it would be we needed, for example, 1,000,000 iterations.
```{r}
sim = function(N, numIter = 1000) {
  replicate(numIter, {
    x1 = runif(N)
    d = data.frame(x = x1, y = 10*x1 + 1 + rnorm(N))
    lm(y ~ x^2., d)
  }, simplify = FALSE)
}
sim(2)
```

## Data types
* vector types
* logical, integer, numeric, character, complex
  * in this order as values of one type can be coerced to the next type (to the right) without losing information

```{r}
c(TRUE, 2L) # `TRUE` and `2L` are coerced to an integer value
c(TRUE, 2L, 3.1415)
c(TRUE, 2L, 3.1415)
c(TRUE, 2L, 3.1415, "2.9")
```
* What is class NA?

## Class vs. typeof
* `typeof()` tells us how the object is built
* `class()` gives a human label for how to think about the object
  * methods for printing, plotting, etc.
  * higher-level concept than raw value
```{r}
class(Sys.Date())
```
`typeof()` is useful when getting something returned from a function in a package. This is because the function give insight on what can be done with the returned object.
```{r}
typeof(Sys.Date())
```
```{r}
f = mpg ~ .
class(f)
typeof(f)
```
```{r}
fit = lm(mpg ~ ., mtcars)
class(fit)
typeof(fit)
names(fit)
```
### Attributes

* R objects can have attributes "hanging" off them
  * arbitrary list of name-value pairs
* special recognized attribute names
  * class
  * names
  * dim
  * dimnames
* attributes(x)
```{r error=TRUE}
attr(x, "id")
attr(x, "id") = value
```

The `structure()` function allows full control to set datatypes in r
```{r}
t <- structure(1:3,
          class = "Bob",
          names = c("a", "b", "c"),
          unit = "XXX")
class(t)
names(t)
```

### Dataframes
* Need for collection of columns with capability of different types of each column
* `data.frame` is a list with constraint that all elements/columns have same number of elements/rows/records
* Rarely used matrices except for
  * linear algebra
  * result of `sapply()`
```{r}
head(mtcars, n = 20)
```


### Subsetting
* General rule for base R data types
  * Subsetting an object with p returns an object
* 6 different ways for vector types
  * position/index x[1],x[2:3]
  * negative/index x[-1],x[-(2:3)]- omit elements
  * logical vector:
    * same length as vector being subsetted
    * elements corresponding to TRUE,kept
    * elements corresponding to FALSE, dropped/omitted
  * name
    * x[c("a", "b", "c")]
  * empty
    * all elements. Equivalent to using 1:length(x)
    * x[]
    * given x = 1:10, compare x = 1 and x[] = `
  * can repeat an index or name
